EEOB563 -- Assignment #2

### 2019-01-27 assignments/2/assignment_2.Rmd
Rendered Assignment 2, only pen and paper part missing

---
title: 'EEOB563 -- Assignment #2'
author: "Dennis Psaroudakis"
date: "January 26th 2019"
output:
  pdf_document:
    dev: pdf
    latex_engine: lualatex
    md_extensions: +link_attributes+multiline_tables
    pandoc_args: --listings
mainfontoptions: Numbers=OldStyle
monofont: Linux Libertine Mono O
mainfont: Linux Libertine O
papersize: letter
sansfont: Linux Biolinum O
language: en-US
...

@@

## 4
a) The dinosaur sequence is highly similar to the cloning vector pAgaL as well as some other cloning vectors.
b) The highest rated sequence is erythroid transcription factor from *Gallus gallus*. It is only 96% identical, there are some differences:
```
Query  121   MEFVALGGPDAGSPTPFPDeagaflglgggerteaggllaSYPPSGRVSLVPWADTGTLG  300
             MEFVALGGPDAGSPTPFPDEAGAFLGLGGGERTEAGGLLASYPPSGRVSLVPWADTGTLG
Sbjct  1     MEFVALGGPDAGSPTPFPDEAGAFLGLGGGERTEAGGLLASYPPSGRVSLVPWADTGTLG  60

@@

![Tree created by mafft](./mafftTree.png){width=65%}}

>>>>

---
title: 'EEOB563 -- Assignment #2'
author: "Dennis Psaroudakis"
date: "January 26th 2019"
output:
  pdf_document:
    dev: pdf
    latex_engine: lualatex
    md_extensions: +link_attributes+multiline_tables
    pandoc_args: --listings
mainfontoptions: Numbers=OldStyle
monofont: Linux Libertine Mono O
mainfont: Linux Libertine O
papersize: letter
sansfont: Linux Biolinum O
language: en-US
titlepage: true
...

@@

## 4
a) The dinosaur sequence is highly similar to the cloning vector pAgaL as well as some other cloning vectors.
b) The highest rated sequence is erythroid transcription factor from *Gallus gallus*. It is only 96% identical, there are some differences:

```
Query  121   MEFVALGGPDAGSPTPFPDeagaflglgggerteaggllaSYPPSGRVSLVPWADTGTLG  300
             MEFVALGGPDAGSPTPFPDEAGAFLGLGGGERTEAGGLLASYPPSGRVSLVPWADTGTLG
Sbjct  1     MEFVALGGPDAGSPTPFPDEAGAFLGLGGGERTEAGGLLASYPPSGRVSLVPWADTGTLG  60

@@

![Tree created by mafft](./mafftTree.pdf){width=95%}
